---
title: "Using ggflagsbr: Brazilian State Flags in ggplot2"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ggflagsbr-introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ggflagsbr)
```


#Installation

```{r}
# Install from local development version
devtools::install_github("DATAUNIRIO/ggflagsbr")

# Or load during development
devtools::load_all()

```


Then load the package:

```{r}
library(ggplot2)
library(ggflagsbr)

```

Basic Usage

The core workflow involves:

Creating a dataset with state abbreviations (UF)

Retrieving the corresponding flag image paths

Using *geom_flag_uf()* inside a ggplot

Example 1: Bar chart with flags

```{r}
df <- data.frame(
  uf = c("RJ", "SP", "MG", "BA"),
  value = c(10, 20, 15, 12)
)

df$image <- get_flag_uf(df$uf)

ggplot(df, aes(x = uf, y = value)) +
  geom_col(fill = "grey80") +
  geom_flag_uf(aes(image = image), size = 0.08) +
  theme_minimal()
```


Scatter Plot Example

Flags can also be used in scatter plots:

```{r}
set.seed(123)

df2 <- data.frame(
  uf = c("RJ", "SP", "MG", "RS", "PE"),
  x = runif(5, 0, 10),
  y = runif(5, 0, 10)
)

df2$image <- get_flag_uf(df2$uf)

ggplot(df2, aes(x, y)) +
  geom_flag_uf(aes(image = image), size = 0.1) +
  theme_minimal() +
  labs(
    title = "Scatterplot with Brazilian State Flags"
  )
```



How It Works

The function *get_flag_uf()* retrieves the correct image path from the package's internal inst/flags/ directory.

Internally, it uses:

*system.file("flags", paste0(uf, ".png"), package = "ggflagsbr")*

This ensures that flags are correctly resolved after installation.

Best Practices

Use official IBGE state abbreviations (e.g., RJ, SP, MG).

Future Extensions

Possible improvements include:

Direct aesthetic mapping: aes(uf = uf)

Circular flag rendering

Additional metadata for states

# Conclusion

ggflagsbr extends the expressive power of ggplot2 by enabling
state-level visual identity in data visualization workflows.
